FinalManuscript_DISCS_UG

### 2019-01-08 parts/01_introduction_03objectives.tex

Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and DGK cryptosystems to perform linear operations on encrypted data. In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

In summary, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
    \item Create a library for the Open Source Computer Vision Library (OpenCV) to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

>>>>

Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data. In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

In summary, in this study, we wish to
\begin{enumerate}
    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
    \item Create a library for the Open Source Computer Vision Library (OpenCV) to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

### 2019-01-08 parts/04_results.tex

\chapter{RESULTS AND DISCUSSION}
After implementing your methodology and gathering all pertinent data, in this section, you will now present the gathered data to your reader. By the end of this section, your reader should have an idea of what exactlty happened during the experiment. 
A good way to organize your results is to group them is to present them in the same order which your methodology was presented. For instance, if your methodology included the analysis of user logs, the implementation of an application, and the testing of this application, your results should flow in the same way. In addition, more often than not, you will be presenting a large volume of data, so utilize figures and tables whenever appropriate. Table 5.1 below presents one way of how to go about presenting your data. Note the table caption and headers, as mentioned in our framework.

@@

There are, however, some additional notes that must be clarified. First, given that you will be gathering a huge volume of data, you must be able to classify which of these were critical in determining the outcome of your study, and which ones need not be presented. The critical data must be presented in this section, while the minor ones may be placed in the Appendices of your paper, which will be described later in this template.

Another clarification to be noted is that the presentation of results in this section must be objective, or `as-is'. This means that you must describe your results in a way understandable to your reader without putting any form of interpretation. In effect, this section’s intent is to provide answers to ``what happened'' questions, not ``what does it mean'' questions. The interpretation of results is the subject of a later section.

Finally, because this is a presentation of what happened in the past, all tenses used in this section must be in the past form, be it active or passive. This will also be true for the preceeding sections after the study’s implementation, especially when stating the methodology.

>>>>

\chapter{RESULTS AND DISCUSSION}
% After implementing your methodology and gathering all pertinent data, in this section, you will now present the gathered data to your reader. By the end of this section, your reader should have an idea of what exactlty happened during the experiment. 
% A good way to organize your results is to group them is to present them in the same order which your methodology was presented. For instance, if your methodology included the analysis of user logs, the implementation of an application, and the testing of this application, your results should flow in the same way. In addition, more often than not, you will be presenting a large volume of data, so utilize figures and tables whenever appropriate. Table 5.1 below presents one way of how to go about presenting your data. Note the table caption and headers, as mentioned in our framework.

% \begin{table}[t]
% \centering
% \caption {Preliminary Test Result, organized by Problem Type}
% \label{tab:acc_lit} 
% \begin{tabular}{ c  c  c  c  c  c  c  c  c  c  c }
% \hline
% Problem	&Average 	&Standard 	&Average 		&Standard		&Dominant\\
% Type  &Steps   &Deviation   &Duration   &Deviation   &Affective\\
%   &   &(Steps)   &(s)   &(Duration)   &State\\ \hline

% A1  &14   &2.30   &23.04   &3.50   &CONF\\
% A2  &2   &5.36   &32.10   &2.01   &FLOW\\
% A3  &31   &1.01   &28.55   &4.03   &FLOW\\
% B1  &24   &4.40   &45.30   &3.30   &BOR\\
% B2  &33   &2.12   &20.56   &2.21   &FLOW\\
% B3  &36   &1.05   &LOSE   &1.15   &CONF\\
% C1  &22   &1.33   &LOSE   &1.40   &FLOW\\
% C2  &23   &3.03   &LOSE   &1.30   &FLOW\\
% D1  &30   &1.79   &LOSE   &1.45   &FLOW\\
% D2  &15   &1.30   &LOSE   &1.05   &FLOW\\ \hline
% \end{tabular}
% \end{table}

% There are, however, some additional notes that must be clarified. First, given that you will be gathering a huge volume of data, you must be able to classify which of these were critical in determining the outcome of your study, and which ones need not be presented. The critical data must be presented in this section, while the minor ones may be placed in the Appendices of your paper, which will be described later in this template.

% Another clarification to be noted is that the presentation of results in this section must be objective, or `as-is'. This means that you must describe your results in a way understandable to your reader without putting any form of interpretation. In effect, this section’s intent is to provide answers to ``what happened'' questions, not ``what does it mean'' questions. The interpretation of results is the subject of a later section.

% Finally, because this is a presentation of what happened in the past, all tenses used in this section must be in the past form, be it active or passive. This will also be true for the preceeding sections after the study’s implementation, especially when stating the methodology.

@@
